% Template for IEEEtransactions
% Adapted by Sik in March 2016 to meet his requirements
%
\documentclass[10pt,conference]{latex/ieeeconf}
%% Latex documents that need direct input
%
\input{./latex/filesystem/ieee_packages.tex}  % contains the latex packages for IEEEtrans
\input{./latex/filesystem/package.tex}        % contains the latex packages
% \input{./latex/filesystem/package_edition.tex}% contains the latex packages
% \usepackage[numbers]{natbib}
\input{latex/filesystem/fileSetup.tex}        % contains package and variables init.
\input{content/acronym_definition.tex}      % contains the acronims

%% Select inputing only one part of the document
%\includeonly{content/intro/intro}   % the file wihtout .tex
%\includeonly{content/other/other_content}

% \addbibresource{./content/lit_review.bib}
% \addbibresource{./content/biblatex-examples.bib}

%% Include all macros below

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}

%% END MACROS SECTION

\begin{document}
\input{content/frontmatter.tex}             % contains the Title and Autor info

\maketitle

% Please keep the abstract below 300 words
\begin{abstract}
This paper deals with the automated detection of \gls{dme} on \gls{oct} volumes.
Our method considers a generic classification pipeline with preprocessing for noise removal and flattening of each B-Scan.
Features such as \gls{hog} and \gls{lbp} are extracted and combined to create a set of different feature vectors which are fed to a linear-\gls{svm} Classifier.
Experimental results show a promising sensitivity/specificity of 0.75/0.87 on a challenging dataset.
\end{abstract}

%\begin{keywords}
%  \glsresetall % reset the acronyms from the abstract
%  \gls{dme},
%  \gls{sdoct},
%  \gls{ml},
%  benchmark,
%\end{keywords}

% \linenumbers

%% Incldue the content without .tex extension
\glsresetall % reset the acronyms from the abstract
\include*{content/intro/intro}          % the file wihtout .tex
\include*{content/survey/relatedwork}
\include*{content/method/dataset}
\include*{content/method/method}
\include*{content/results/results}

\section{Discussion and Conclusion}\label{sec:dis-con}

We presented an automatic classification framework for \gls{sdoct} volumes in order to indentify \gls{dme} volumes versus normal Volumes.
In this regard, we investigated a generic pipeline including preprocessing, feature extraction and feature reduction and feature combination.
The best results were obtained for \gls{hog} feature vectors.
We plan to extend our work with a \gls{bow} approach as well as we intend to study other classifiers (\gls{rbf}-\gls{svm}, \gls{rf}) in a near future.
Also, we are currently working on the extension of the dataset so as to make it more challengeable and open to the community.

\section{Acknowledgment}
The authors would like to acknowledge the financial support of the PHC Merlion from France and Singapore.
The authors would like to acknowledge the Regional Burgundy Council which partially financially supported the current project under the PARI scheme 2.



% \nolinenumbers

%\section*{References}
% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}
%
% OR
%
% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here.

% % Imports the bibliography file "sample.bib"
% \bibliography{sample}
\bibliographystyle{IEEEtran}
\IEEEtriggeratref{10}
\bibliography{content/bib/literature_review,content/bib/retinopathy-bibtex/retinopathy-bibtex,content/bib/i2cvb-retinopathy-bibtex/i2cvb-retinopathy-bibtex}

\end{document}
